---
title: "R Basics"
author: "Justin Ho"
date: "10/11/2017"
output:
  html_document:
    keep_md: true
    self_contained: true
---

# This is a title

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R is simply a calculator, you can perform simple computation by typing the equation.
```{r}
3+4
```

You can define a new object with the assignment operator "<-".
```{r}
result <- 3+4+1
```

When defining a object, nothing will happen when sucessful (no news is good news). To view the object, you can simply type the name of the object.
```{r}
result
```

You can also put string inside an object, remember the quotation mark.
```{r}
text <- "This is a test message again"
```

To view it, type the name of the object.
```{r}
text
```

A vector is a sequence of data elements, we can use "c()" to define a vector.
```{r}
vector <- c(1, 2, 5, 7, 8, 9, 10, 100)
vector
```

You can access a particular compenent of a vector (or many other object types) by using the slicing operator "[]".
```{r}
vector[1] # It shows the first element.
vector[3] # It shows the third element.
vector[1:3] # It shows elements from the first to the second one.
vector[-1] # It shows all the elements EXCEPT the first one.
```

A function is a group of prewritten codes, it takes in data and produces output. For example, "summary()" is a often used function.
```{r}
summary(vector)
```

If you are calling a gigatic object, you don't want to mess up your screen, you might use "head()" to shows the first few components/lines.
```{r}
tail(vector, 3)
```

To know what a function does, use "?" .
```{r}
?head
```

Most functions take in extra arguments too.
```{r}
head(vector, 2) # showing the first two components
```

It works for vector of strings too.
```{r}
textvector <- c("This", "is", "a", "test", "message", ".")
textvector
textvector[2]
head(textvector, 3)
summary(textvector)
```

You can nest the function like this.
```{r}
summary(head(vector, 2))
```

Alternatively, if you load the magrittr package, you can pipe it. It does the same thing, but is written in a slightly amiable way.
```{r}
library(magrittr)
head(vector) %>% summary()
```

